Non-convergence in iterative imputation

### 2025-04-10 Manuscript/manuscript.qmd
clean up repo

---
title: "Non-convergence in iterative imputation"
author: "H. I. Oberman"
abstract: "Iterative imputation has become the de facto standard to accommodate for the ubiquitous problem of missing data. While it is widely accepted that this technique can yield valid inferences, these inferences all rely on algorithmic convergence. Our study provides insight into identifying non-convergence in iterative imputation algorithms. We show that these algorithms can yield correct outcomes even when a converged state has not yet formally been reached. In the cases considered, inferential validity is achieved after five to ten iterations, much earlier than indicated by diagnostic methods. We conclude that it never hurts to iterate longer, but such calculations hardly bring added value."
# keywords: "missing data, iterative imputation, non-convergence, MICE"
# bibliography: references.bib
bibliography: references.bib
---

>>>>

---
title: "Non-convergence in iterative imputation"
author: "H. I. Oberman"
abstract: "Iterative imputation has become the de facto standard to accommodate for the ubiquitous problem of missing data. While it is widely accepted that this technique can yield valid inferences, these inferences all rely on algorithmic convergence. Our study provides insight into identifying non-convergence in iterative imputation algorithms. We show that these algorithms can yield correct outcomes even when a converged state has not yet formally been reached. In the cases considered, inferential validity is achieved after five to ten iterations, much earlier than indicated by diagnostic methods. We conclude that it never hurts to iterate longer, but such calculations hardly bring added value."
# keywords: "missing data, iterative imputation, non-convergence, MICE"
# bibliography: references.bib
bibliography: references.bib
format: pdf
---
